Title Goes Here

### 2020-03-23 analysis/paper/paper.Rmd
Adding 1 sentence

We are also interested in whether there is a variation in topic choices between the two biological genders in archaeological conferences. 
To do this we have used the process of topic modeling, which is used to find natural groups of words when we do not have a specific criteria or simply unsure what we are looking for. There are many ways to accomplish topic modeling, we have used the method of Latent Dirichlet allocation (LDA). This method is beneficial in our case because LDA does not treat one topic, which consists of many words, as seperate from another topic. Before we can start using LDA, we have to first find the number of groups that we need to predetermine. To do this we have used the package ldatuning, which allows us to use multiple methods at once to find the optimal number of groups that we should use for LDA processing. With the number of groups figured out, we then create a topic model based on the number of topics determined, from this we can then assign the words a probability based on its per-topic-per-word probability, which we call beta. After this we filter out only the top 10 terms within each group to keep so that we have the keywords that occur the most by probability. From this we then have top terms from the topics of the conferences. We are only interested in keywords that are meaningful in a topic, therefore we have excluded words that are common in the field of archaeology or simply meaningless, for example, the, a, el, al, archaeology...etc. After figuring out the top terms, we can combine them with our earlier exploration of gender to see if one gender seems to favor another, for example if female or male favor topics about 'rock'.

>>>>

We are also interested in whether there is a variation in topic choices between the two biological genders in archaeological conferences. 
To do this we have used the process of topic modeling, which is used to find natural groups of words when we do not have a specific criteria or simply unsure what we are looking for. There are many ways to accomplish topic modeling, we have used the method of Latent Dirichlet allocation (LDA). This method is beneficial in our case because LDA does not treat one topic, which consists of many words, as seperate from another topic. Before we can start using LDA, we have to first find the number of groups that we need to predetermine. To do this we have used the package ldatuning, which allows us to use multiple methods at once to find the optimal number of groups that we should use for LDA processing. With the number of groups figured out, we then create a topic model based on the number of topics determined, this will put words into groups that most frequently occur together, from this we can then assign the words a probability based on its per-topic-per-word probability, which we call beta. After this we filter out only the top 10 terms within each group to keep so that we have the keywords that occur the most by probability. From this we then have top terms from the topics of the conferences. We are only interested in keywords that are meaningful in a topic, therefore we have excluded words that are common in the field of archaeology or simply meaningless, for example, the, a, el, al, archaeology...etc. After figuring out the top terms, we can combine them with our earlier exploration of gender to see if one gender seems to favor another, for example if female or male favor topics about 'rock'.
